%========================================
% MASTER CV - ANAY PANDYA (v2)
%========================================
\documentclass[10pt,a4paper,sans]{moderncv}

% Style and color
\moderncvstyle{classic}
\moderncvcolor{blue}

% Character encoding
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{3.2cm}

%----------------------------------------
% PERSONAL INFORMATION
%----------------------------------------
\name{ANAY}{PANDYA}
\title{CSE (Cybersecurity) Student | National Forensic Sciences University}
\address{Gandhinagar, Gujarat, India}{382007}
\phone[mobile]{+91~89051~51222}
\email{dearanayji@gmail.com}
\homepage{adper.me}
\social[github]{ADPer0705}
\social[linkedin]{dearanayji}
\extrainfo{Medium: \httplink{medium.com/@adper0705}}
% \photo[70pt][0.4pt]{yourphoto} % optional; disabled for clean layout
\quote{"CSE (Cybersecurity) student at NFSU focused on the intersection of AI and security."}

%----------------------------------------
\begin{document}
\makecvtitle

%----------------------------------------
% SUMMARY / OBJECTIVE
%----------------------------------------
\section{Profile}
Third-year B.Tech-M.Tech (Cybersecurity) student at NFSU specializing in the intersection of AI, automated security, and digital forensics. Experienced in architecting robust solutions ranging from serverless cloud compliance frameworks to LLM-driven intelligence tools and forensic analysis systems. Passionate problem-solver, Linux enthusiast, and active community leader as Co-Founder of the NFSU AI/ML Club.

\begin{itemize}
  \item \textbf{Cybersecurity \& Forensics:} Cloud security automation, anti-forensics detection, and applied cryptography.
  \item \textbf{AI \& Engineering:} Retrieval-Augmented Generation (RAG), local LLM deployments, and full-stack system architecture.
\end{itemize}


%----------------------------------------
% EDUCATION
%----------------------------------------
\section{Education}
\cventry{2023--2028}{Integrated B.Tech + M.Tech in Computer Science and Engineering (Cybersecurity)}{National Forensic Sciences University}{Gandhinagar, Gujarat}{}{
  \begin{itemize}
    \item Current Semester: 6
    \item Cumulative Performance Index (CPI): 8.95 / 10.0
    \item Semester-wise SPI: 8.20, 9.05, 8.30, 8.95, 8.95 % (Optional: keep or remove)
  \end{itemize}
}


%----------------------------------------
% TECHNICAL SKILLS
%----------------------------------------
\section{Technical Skills}
\cvitem{Languages}{Python, C/C++, Rust, Bash, JavaScript, HTML/CSS}
\cvitem{AI / Data Science}{LangChain, FAISS, Ollama, RAG, PyTorch, Scikit-learn, Pandas, NumPy, Matplotlib, OpenCV, LLM APIs}
\cvitem{Cloud \& Web}{AWS (Lambda, EventBridge, SAM), Boto3, FastAPI, React, WebSockets}
\cvitem{Dev \& Databases}{Linux (Debian, Kali), Git, Docker, SQL Server, Entity Framework Core, Tauri}
\cvitem{Domains}{Cybersecurity, Machine Learning, Cloud Security, Digital Forensics, Systems Programming}

%----------------------------------------
% PROJECTS
%----------------------------------------
\section{Projects}

\cventry{2026}{\textbf{ChronoTrace - NTFS Anti-Forensics Detection Framework}}{GitHub: \href{https://github.com/GR4Y-SCALE/ChronoTrace}{\texttt{GR4Y-SCALE/ChronoTrace}}}{}{}{
\begin{itemize}
    \item Engineered an advanced forensic analysis tool for detecting timestamp manipulations and log evasion via post-mortem image analysis and real-time live monitoring.
    \item Implemented custom deterministic anti-forensics rules evaluating \$MFT, USN Journal, and \$LogFile NTFS structures.
    \item \textbf{Tech Stack:} Python, FastAPI, React 19, WebSockets, libewf
\end{itemize}
}

\cventry{2026}{\textbf{RBIH IITD Tryst Hackathon}}{GitHub: \href{https://github.com/ADPer0705/RBIH-IITD-Tryst-Hackathon}{\texttt{ADPer0705/RBIH-IITD-Tryst-Hackathon}}}{}{}{
\begin{itemize}
    \item Developed Comprehensive Exploratory Data Analysis (EDA) Jupyter Notebooks and Reports for the National Fraud Prevention Challenge.
    \item Built and analyzed datasets focusing on digital transaction security and fraud-detection using statistical modelling techniques.
    \item \textbf{Tech Stack:} Python, Jupyter Notebook, Pandas, Matplotlib, HTML, Data Analysis
\end{itemize}
}

\cventry{2026}{\textbf{MerkleWatch - Cryptographic Integrity Tool}}{GitHub: \href{https://github.com/ADPer0705/MerkleWatch}{\texttt{ADPer0705/MerkleWatch}}}{}{}{
\begin{itemize}
    \item Developed a CLI-first utility for creating deterministic, tamper-evident directory snapshots using Merkle trees and SHA-256 hashing.
    \item Implemented domain separation and chunked reading (64KB) for memory-efficient processing of large files, along with customizable ignore rules.
    \item \textbf{Tech Stack:} Python, Cryptography (SHA-256), File System Operations
\end{itemize}
}

\cventry{2026}{\textbf{Wordsmith - Contextual Dictionary Generator}}{URL: \href{https://adper.me/wordsmith}{\texttt{adper.me/wordsmith}}}{}{}{
\begin{itemize}
    \item Engineered an AI-driven contextual dictionary and wordlist generator tailored for security professionals.
    \item Integrated multiple LLM providers (Groq, Gemini, OpenAI) to automatically extract relevant tokens from unstructured raw intelligence.
    \item \textbf{Tech Stack:} JavaScript/HTML/CSS, Multiple LLM APIs (Groq, Gemini, OpenAI)
\end{itemize}
}

\cventry{2025}{\textbf{OverPage - AI Webpage Analyzer}}{GitHub: \href{https://github.com/ADPer0705/OverPage}{\texttt{ADPer0705/OverPage}}}{}{}{
\begin{itemize}
    \item Developed a Chrome extension designed to scrape active webpages and generate on-demand summaries via an integrated chat interface.
    \item Engineered a PHP backend to handle text preprocessing and forward client queries directly to the \textbf{Google Gemini API}, minimizing local resource consumption.
    \item \textbf{Tech Stack:} HTML/CSS/JavaScript (Chrome Extension), PHP, Google Gemini API
\end{itemize}
}

\cventry{2025}{\textbf{Praetor - Serverless AWS Security Automation}}{GitHub: \href{https://github.com/ADPer0705/praetor}{\texttt{ADPer0705/praetor}}}{}{}{
  \begin{itemize}
    \item Engineered a serverless compliance auditing platform using \textbf{AWS Lambda and EventBridge} to perform 170+ daily security checks across 11 AWS services.
    \item Delivered zero-cost, enterprise-grade cloud security scanning through automated HTML dashboards and Slack integration for critical misconfigurations.
    \item \textbf{Tech Stack:} Python, AWS (Lambda, EventBridge, CloudTrail, SAM), Boto3
  \end{itemize}
}

\cventry{2025}{\textbf{ADB Data Fetcher Utility}}{GitHub: \href{https://github.com/ADPer0705/ADB_Data_Fetcher}{\texttt{ADPer0705/ADB\_Data\_Fetcher}}}{}{}{
  \begin{itemize}
    \item Developed a Windows Form desktop application using \textbf{C\# (.NET 8.0)} to automate the extraction of SMS, contacts, and logs from Android devices via ADB.
    \item Integrated Entity Framework Core with SQL Server to provide seamless persistence and management of device data.
    \item \textbf{Tech Stack:} C\#, Windows Forms, Entity Framework Core, SQL Server, ADB
  \end{itemize}
}

\cventry{2025}{\textbf{TeleDM - Telegram Download Manager}}{GitHub: \href{https://github.com/ADPer0705/TeleDM}{\texttt{ADPer0705/TeleDM}}}{}{}{
  \begin{itemize}
    \item Developed a feature-rich desktop application enabling robust, interrupt-tolerant file downloads from Telegram without keeping the client active.
    \item Implemented a Tkinter GUI featuring queue management, progress tracking, auto-resume capabilities, and a SQLite database for persistent download history.
    \item \textbf{Tech Stack:} Python, Tkinter, SQLite, Telegram API
  \end{itemize}
}

\cventry{2024}{\textbf{Inquiro - Local RAG System}}{GitHub: \href{https://github.com/CY-N4P5E/Inquiro}{\texttt{CY-N4P5E/Inquiro}}}{}{}{
    \begin{itemize}
    \item Built a \textbf{RAG system} transforming documents into a queryable knowledge base using \textbf{LangChain} and \textbf{FAISS}.
    \item Implemented a local-first architecture with \textbf{local LLMs (Mistral)} via Ollama, along with Nomic Embed Text for high-quality semantic understanding and optimized memory management.
    \item \textbf{Tech Stack:} Python, LangChain, Ollama, FAISS, Nomic Embeddings
\end{itemize}
}

\cventry{2024}{\textbf{AIML CTF Challenges}}{GitHub: \href{https://github.com/ADPer0705/AIML_CTF}{\texttt{ADPer0705/AIML\_CTF}}}{}{}{
  \begin{itemize}
    \item Designed and developed original Capture-the-Flag (CTF) challenges focusing on AI/ML and Cryptography for the university club.
    \item Created scenarios including machine learning model bias detection and Python reverse engineering to train students on practical security implementations.
    \item \textbf{Tech Stack:} Python, Jupyter Notebook
  \end{itemize}
}

%----------------------------------------
% EXPERIENCE / INTERNSHIPS
%----------------------------------------
\section{Experience}
\cventry{May--July 2025}{Intern / Research Assistant}{Department of Telecommunications, NFSU}{Gandhinagar}{}{
  \begin{itemize}
    \item Selected through a competitive university exam; the only student from my class and the youngest overall to qualify.
    \item Conducted research on the security posture of 5G architecture, with a focus on subscriber information security vulnerabilities.
    \item Developed a Retrieval-Augmented Generation (RAG) application, feeding it 5G technical specifications from 3GPP to enable an interactive query interface.
    \item Gained hands-on experience in cybersecurity research, technical documentation, and applied AI integration.
  \end{itemize}
}

\cventry{Jul 2024}{Cybersecurity Intern}{Centre for Development of Advanced Computing (C-DAC), India}{}{}{
  \begin{itemize}
    \item Completed an intensive training program on cybersecurity fundamentals.
    \item Executed hands-on labs in network security, digital forensics, and ethical hacking.
    \item Gained practical experience with tools like Wireshark, FTK Imager, and Metasploit.
  \end{itemize}
}


%----------------------------------------
% CERTIFICATIONS / COURSES
%----------------------------------------
\section{Certifications}
\cvitem{Mar 2026}{Fortinet Certified Fundamentals Cybersecurity -- Fortinet}
\cvitem{Mar 2026}{Technical Introduction to Cybersecurity 3.0 -- Fortinet}
\cvitem{Mar 2026}{Introduction to the Threat Landscape 3.0 -- Fortinet}
\cvitem{Dec 2024}{Certified in CC -- (ISC)\textsuperscript{2}}
% \cvitem{Apr 2024}{Google Cloud Computing Foundations Certificate -- Google Cloud}
% \cvitem{Apr 2024}{Build a Secure Google Cloud Network Skill Badge -- Google Cloud}
% \cvitem{Apr 2024}{Implement Load Balancing on Compute Engine Skill Badge -- Google Cloud}
% \cvitem{Apr 2024}{Prepare Data for ML APIs on Google Cloud Skill Badge -- Google Cloud}
% \cvitem{Apr 2024}{Set Up an App Dev Environment on Google Cloud Skill Badge -- Google Cloud}


%----------------------------------------
% LEADERSHIP / POSITIONS OF RESPONSIBILITY
%----------------------------------------
\section{Leadership \& Activities}
\cvitem{2024--Present}{Co-Founder / Tech Lead – AI/ML Club, National Forensic Sciences University
  \begin{itemize}
    \item Initiated the creation of the AI/ML Club and actively manage the DataCamp classroom for the university community.
    \item Played a key role as part of the tech team, organizing workshops, lectures, and hands-on sessions on AI implementation and its real-world applications.
    \item Designed and conducted a Capture-the-Flag (CTF) challenge, including creating original problems for participants.
    \item Delivered live demonstrations and interactive programming sessions, educating students on AI/ML project development.
  \end{itemize}
}


%----------------------------------------
% INTERESTS
%----------------------------------------
\section{Interests}
\cvitem{Professional}{
  Cybersecurity, Artificial Intelligence \& Machine Learning, Intelligent Security Systems, Linux Customization, Workflow Automation
}
\cvitem{Personal}{
  Tinkering with hardware/software, Gaming, Writing, Open-Source Contribution, Building towards a Stark-style personal workstation
}

%----------------------------------------
\end{document}